Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-09-23 referee.tex
minor note
Adding some notes to the report (just to keep track of my thoughts)
adding changes to fix merge problem.

\begin{figure}[ht!]
	\centering
	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_halo_mass.pdf}
  \caption{\label{fig:compare_mass} \jhw{Include caption.}}
\end{figure}

@@

-Fraction of halos that halo Pop III stars forming outside the halos: Turns out I was not able to get this data as easily as I thought. I am going to quickly run through my script and find the P3 stars in each dataset which are not in halos.

>>>>

\begin{figure}[ht!]
	\centering
	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_mass_ratio.pdf}
  \caption{\label{fig:compare_mass} The Rockstar mass multiplied by $\Omega_{\rm M} / \Omega_{\rm DM}$ versus the Machacek+01 method of calculating halo mass. The bottom panel is the ratio of the Rockstar mass to the calculated mass versus the calculated mass. The Rockstar mass tends to lie just above the 1:1 relation, implying that the halo masses are comparable. For the case where the calculated mass is much larger than the rockstar mass, this occurs when the halos are subhalos of a larger halo.}
\end{figure}

@@

1\% of Pop III stars form outside the halo. This has been added to the Population III Host Halo Masses subsection.

Figure \ref{fig:avg_baryon_fraction} show the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.

\begin{figure}[ht!]
  \centering
  \includegraphics[keepaspectratio=true, scale=0.4]{images/avg_baryon_fraction.pdf}
  \caption{\label{fig:avg_baryon_fraction} Average baryon fraction within each halo versus the corresponding halo mass. The solid line indicates the cosmic baryon fraction of 0.154.}
\end{figure}
